ms_tables

### 2018-11-16 analysis/evi/explore_resilience.Rmd
update

---
title: "Explore resilience evi"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Aug"
output: 
  md_document:
    variant: markdown_github
---
```{r, echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(fig.align='center', message = FALSE, warning = FALSE) 
```

@@

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library('dplyr')
library('tidyverse')
library('broom')
library('pander')
library('lsmeans')
library('effects')
library('gridExtra')
library('WRS2')
library('car')
library('MASS')
library('rcompanion')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
```

@@

```{r}
# Read data
raw_evires <- read.csv(file=paste(di, "/data/resilience/resilience_evi.csv", sep=""), header = TRUE, sep = ',')

# add data of pop
anomalias <- read.csv(file=paste(di, "/data/anomalies/anomalias_evimean.csv", sep=""), header = TRUE, sep = ',')

@@

```{r, echo=FALSE}
pdf(paste0(di, '/out/mean_resilience/evi/interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(paste0(di, '/out/mean_resilience/evi/interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()
```

@@

write.csv(aovas_coeff, file=paste0(di, '/out/anovas_resilience/evi/anovas_statistics.csv'), row.names = F)

@@

write.csv(aovas_model_summary, 
          file=paste0(di, '/out/anovas_resilience/evi/anovas_summary_modelos.csv'), row.names = F)

@@

```{r}
normtestA <- rbind(nrcA, nrtA, nrsA, nrrsA) 
normtestA %>% pander()
write.csv(normtestA, 
          file=paste0(di, '/out/anovas_resilience/evi/normo_disturb_year.csv'), row.names = F)
```

```{r}
normtestB <- rbind(nrcB, nrtB, nrsB, nrrsB) 
normtestB %>% pander()
write.csv(normtestB, 
          file=paste0(di, '/out/anovas_resilience/evi/normo_site.csv'), row.names = F)
```

```{r}
normtestAB <- rbind(nrcAB, nrtAB, nrsAB, nrrsAB) 
normtestAB%>% pander()
write.csv(normtestAB, 
          file=paste0(di, '/out/anovas_resilience/evi/normo_disturb_year_site.csv'), row.names = F)
```

@@

homo %>% pander()
write.csv(homo, 
          file=paste0(di, '/out/anovas_resilience/evi/homocedasticidad.csv'), row.names = F)
```

@@

homo_log %>% pander()
write.csv(homo_log, 
          file=paste0(di, '/out/anovas_resilience/evi/homocedasticidad_log.csv'), row.names = F)
```

@@

homo_log1 %>% pander()
write.csv(homo_log, 
          file=paste0(di, '/out/anovas_resilience/evi/homocedasticidad_log_plus_1.csv'), row.names = F)
```

@@

pdf(paste0(di, '/out/resilience_robust/evi/robust_plot_evi_drought.pdf'), width=9, height = 9)
robust_plot_evi_drought 
dev.off()
```

@@

pdf(paste0(di, '/out/resilience_robust/evi/robust_plot_evi_site.pdf'), width=9, height = 9)
robust_plot_evi_site 
dev.off()
```

@@

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_mhuber_agg_b.csv'), row.names = F)

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_pairwise.csv'), row.names = F)
write.csv(trimmedanovas, file=paste0(di, '/out/anovas_resilience/huber_evi/trimmed_anovas.csv'), row.names = F)
```

>>>>

---
title: "Explore resilience evi"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Aug"
output: 
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---
```{r, echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(fig.align='center', message = FALSE, warning = FALSE) 
```

@@

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library('dplyr')
library('here')
library('tidyverse')
library('broom')
library('pander')
library('lsmeans')
library('effects')
library('gridExtra')
library('WRS2')
library('car')
library('MASS')
library('rcompanion')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
```

@@

```{r}
# Read data
raw_evires <- read.csv(here::here("/data/resilience","resilience_evi.csv"), header = TRUE, sep = ',')

# add data of pop
anomalias <- read.csv(here::here("/data/anomalies", "anomalias_evimean.csv"), header = TRUE, sep = ',')

@@

```{r, echo=FALSE}
pdf(here::here('/out/mean_resilience/evi', 'interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(here::here('/out/mean_resilience/evi','interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()
```

@@

write.csv(aovas_coeff, file=here::here('/out/anovas_resilience/evi', 'anovas_statistics.csv'), row.names = F)

@@

write.csv(aovas_model_summary, 
          file=file=here::here('/out/anovas_resilience/evi','anovas_summary_modelos.csv'), row.names = F)

@@

```{r}
normtestA <- rbind(nrcA, nrtA, nrsA, nrrsA) 
normtestA %>% pander()
write.csv(normtestA, 
          file=here::here('/out/anovas_resilience/evi','normo_disturb_year.csv'), row.names = F)
```

```{r}
normtestB <- rbind(nrcB, nrtB, nrsB, nrrsB) 
normtestB %>% pander()
write.csv(normtestB, 
          file=here::here('/out/anovas_resilience/evi','normo_site.csv'), row.names = F)
```

```{r}
normtestAB <- rbind(nrcAB, nrtAB, nrsAB, nrrsAB) 
normtestAB%>% pander()
write.csv(normtestAB, 
          file=here::here('/out/anovas_resilience/evi','/normo_disturb_year_site.csv'), row.names = F)
```

@@

homo %>% pander()
write.csv(homo, 
          file=here::here('/out/anovas_resilience/evi','homocedasticidad.csv'), row.names = F)
```

@@

homo_log %>% pander()
write.csv(homo_log, 
          file=here::here('/out/anovas_resilience/evi','homocedasticidad_log.csv'), row.names = F)
```

@@

homo_log1 %>% pander()
write.csv(homo_log, 
          file=here::here('/out/anovas_resilience/evi','homocedasticidad_log_plus_1.csv'), row.names = F)
```

@@

pdf(here::here('/out/resilience_robust/evi/','robust_plot_evi_drought.pdf'), width=9, height = 9)
robust_plot_evi_drought 
dev.off()
```

@@

pdf(here::here('/out/resilience_robust/evi/', 'robust_plot_evi_site.pdf'), width=9, height = 9)
robust_plot_evi_site 
dev.off()
```

@@

```{r}
# Export data 
write.csv(mhuber, file=here::here('/out/anovas_resilience/huber_evi','robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=here::here('/out/anovas_resilience/huber_evi','robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=here::here('/out/anovas_resilience/huber_evi','robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=here::here('/out/anovas_resilience/huber_evi','robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=here::here('/out/anovas_resilience/huber_evi','robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=here::here('/out/anovas_resilience/huber_evi','robust_mhuber_agg_b.csv'), row.names = F)

write.csv(pairwise, file=here::here('/out/anovas_resilience/huber_evi','/robust_pairwise.csv'), row.names = F)
write.csv(trimmedanovas, file=here::here('/out/anovas_resilience/huber_evi','trimmed_anovas.csv'), row.names = F)
```

### 2018-11-16 man/ms_tables/t_huber_res_bai.Rmd
update

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
---

@@

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
```

@@

```{r, echo = FALSE, warning = FALSE}
mraw <- df <- read.csv(here("/out/anovas_resilience/huber_bai", "robust_mhuber_agg.csv"), header = TRUE)

m <- mraw %>% 
  filter(var != 'rrs') %>% 
  rename(variables = var)  %>% 
  dplyr::select(c(-n, -Letter)) %>% 
 unite("mh", c("M.Huber", "ci"), sep = "\n")

>>>>

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
editor_options: 
  chunk_output_type: console
---

@@

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
```

@@

```{r, echo = FALSE, warning = FALSE}
mraw <- read.csv(here::here("/out/anovas_resilience/huber_bai", "robust_mhuber.csv"), header = TRUE)

m <- mraw %>% 
  filter(var != 'rrs') %>% 
  rename(variables = var)  %>% 
  dplyr::select(c(-n, -Letter, -MonoLetter, -var_sorted)) %>% 
  mutate_at(.vars = c("M.Huber", "lower.ci", "upper.ci"), funs(round(., 3)))

 unite("mh", c("M.Huber", "ci"), sep = "\n")
